Large Language Models in Reinforcement Learning - A Comparison of Methods

### 2023-11-09 doc/paper.tex
update paper
Signed-off-by: Jonatan Hanssen <jonatan.hanssen@outlook.com>

We would like to acknowledge the ROBIN research group at the University of Oslo Dept. of Informatics, who have arranged for us to be able to undertake this research and gain valuable experience. In particular, we would like to thank our supervisors Katrine Nergård and Kai Olav Ellefsen for their help and guidance in this project.

@@

\begin{table}[h]
\caption{PPO hyperparameters}
\begin{center}
\label{hyperparams_transposed}
\begin{tabular}{c | c}
Parameter & Value \\
\hline
Gamma & 0.99 \\
Steps per episode & 1024 \\
Epochs per episode & 10 \\
Batches per epoch & 8 \\
PPO Clipping value & 0.2 \\
Value loss coefficient & 0.3 \\
Entropy coefficient. & 0 \\
Learning rate & 3.0e-4 \\
\end{tabular}
\end{center}
\end{table}

>>>>

We would like to acknowledge the ROBIN research group at the University of Oslo Department of Informatics, who have arranged for us to be able to undertake this research and gain valuable experience. In particular, we would like to thank our supervisors Katrine Nergård and Kai Olav Ellefsen for their help and guidance in this project.

@@

\begin{table}[h]
\caption{PPO hyperparameters}
\begin{center}
\label{hyperparams_transposed}
\begin{tabular}{c | c}
Parameter & Value \\
\hline
Gamma & 0.99 \\
Steps per episode & 1024 \\
Epochs per episode & 10 \\
Batches per epoch & 8 \\
PPO Clipping value & 0.2 \\
Value loss coefficient & 0.3 \\
Entropy coefficient & 0 \\
Learning rate & 3.0e-4 \\
\end{tabular}
\end{center}
\end{table}
